Twists of supersymmetric gauge theories

### 2019-11-08 paper.tex
Current 7d status

\begin{theorem} \label{7d_rank2_twist_thm}
The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with an oriented 1-manifold $L$ is equivalent to mixed Chern-Simons theory on $X_3 \times (L)_{\mr{dR}}$.
\end{theorem}

>>>>

\begin{theorem} \label{7d_rank2_twist_thm}
The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$. \chris{actually I need to think about the twisting homomorphism here.}
\end{theorem}
